Towards Comparable Active Learning

### 2023-04-20 doc/al_benchmark_paper.tex
encoded argument fix
tuned usps

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{State Space}
{\color{red} Version: 0.1}\\
Since every AL agent needs a different state space our environment exposes a full state to the agent, so that the agent has full control of what information will be used. \\ [1mm]
The state can include the following information:
\begin{itemize}
	\item The entire labeled dataset $\mathcal{L}^{(i)}$
	\item The entire unlabeled dataset $\mathcal{U}^{(i)}$
	\item A histogram of labeled points per class (count)
	\item The available budget $B$
	\item Number of added datapoints $|\mathcal{L}| - |\mathcal{S}|$
	\item The initial validation accuracy $\operatorname{acc}^{(0)}$ and current validation accuracy $\operatorname{acc}^{(i)}$
	\item The current classification model including all model weights $\theta^{(i)}$
	\item The current optimizer including it's full state
	\item The current sample of unlabeled points $u^{(i)}$
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Training the Classifier}\label{sec:training_the_classifier}
Generally, the classification model can be trained in two ways. Either you reset the parameters after each AL iteration and train the classifier from scratch with the updated labeled set $\mathcal{L}^{(i)}$, or you retain the previous state and only fine-tune the classifier on $\mathcal{L}^{(i)}$ for a reduced number of epochs.
In this work we use the fine-tuning method for raw datasets to save computation, while we use the from-scratch training for embedded dataset, since they have very small classifiers and this method generally produces better results.
Our fine-tuning scheme always trains for at least one epoch and employs an aggressive early stopping after that.
The early stopping has patience 0, so it will stop as soon as the validation loss does no longer decrease.

@@

>>>>

Manual NIPS Benchmark paper eval (out of 6):
\begin{itemize}
	\item Has new method: 1
	\item Multiple domains: 2
	\item $> 5$ datasets: 3
	\item $> 5$ baselines: 4
\end{itemize}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation Details}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{State Space}
{\color{red} Version: 0.1 Remove analogies to RL}\\
Since every AL agent needs a different state space our environment exposes a full state to the agent, so that the agent has full control of what information will be used. \\ [1mm]
The state can include the following information:
\begin{itemize}
	\item The entire labeled dataset $\mathcal{L}^{(i)}$
	\item The entire unlabeled dataset $\mathcal{U}^{(i)}$
	\item A histogram of labeled points per class (count)
	\item The available budget $B$
	\item Number of added datapoints $|\mathcal{L}| - |\mathcal{S}|$
	\item The initial validation accuracy $\operatorname{acc}^{(0)}$ and current validation accuracy $\operatorname{acc}^{(i)}$
	\item The current classification model including all model weights $\theta^{(i)}$
	\item The current optimizer including it's full state
	\item The current sample of unlabeled points $u^{(i)}$
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Choosing the Classifier}\label{sec:choosing_the_classifier}
Traditionally, the classifier is chosen per dataset so that it is capable of solving the dataset close to the SOTA performance reported in the literature.
Similar to our hypothesis in section \ref{sec:evaluation} we hypothesize that AL algorithms will perform similarly on small classifiers and more complex ones, so that the overall ranking of algorithms stays the same.
{\color{red} TODO: Transform this into full hypothesis incl. formatting?}\\
On the basis of this hypothesis we opt to use smaller classifiers that still solve the dataset to a reasonable degree.
Smaller classifiers also require fewer labeled datapoints to acquire performance close to the upper bound.
This behavior can be observed in Figure {\color{red} TODO}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Training the Classifier}\label{sec:training_the_classifier}
{\color{red} Version: 0.1 Full rework needed}\\
Generally, the classification model can be trained in two ways. Either you reset the parameters after each AL iteration and train the classifier from scratch with the updated labeled set $\mathcal{L}^{(i)}$, or you retain the previous state and only fine-tune the classifier on $\mathcal{L}^{(i)}$ for a reduced number of epochs.
In this work we use the fine-tuning method for raw datasets to save computation, while we use the from-scratch training for embedded dataset, since they have very small classifiers and this method generally produces better results.
Our fine-tuning scheme always trains for at least one epoch and employs an aggressive early stopping after that.
The early stopping has patience 0, so it will stop as soon as the validation loss does no longer decrease.
